MCC_pilot

### 2018-02-06 stats/mcc_pilot.Rmd
updating informativeness

```{r}
# alternative model
lm2 <- glmer(correct ~ change + condition +
              (condition + change + trial|id) + (1|choiceAgent), 
              data = data_cg, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

>>>>

```{r}
#  final model
#  removing random effects for trial as there seems to be no evidence for a trial effect
lm2 <- glmer(correct ~ change + condition +
              (condition + change |id) + (1|choiceAgent), 
              data = data_cg, family = binomial, 
              control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
